Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
update

The rapid growth of social media has made SNSs increasingly attractive targets 
for spam and fraud, leading to a proliferation of sophisticated attacks. This 
trend is reflected in recent research, as papers 
have focused on identifying and classifying the various types of social media spam. 
Many of these studies employ techniques previously used to combat conventional 
email and web spam. SNSs also provide opportunities to take advantage of user 
reputation and other social graph-dependent features to improve classification. 
Nevertheless, most research has been carried out on publicly-available data 
from SNSs, making it difficult up until now to measure the effect of private user 
data on algorithms for detecting site misuse.

@@

Gao et al. \cite{gao} look at Facebook wall posts, analyzing temporal properties, 
URL characteristics, post ratios and other features of malicious accounts. They 
also pinpoint various spam ``campaigns" based on products advertised in a given 
time frame. They note that spam on Facebook often exhibits burstiness and is mainly 
sent from compromised accounts. Benevenuto et al. \cite{benevenuto} identify 
attributes of spam on video SNSs and use a Support Vector Machine (SVM) for classification.

>>>>

The rapid growth of social media has made SNSs increasingly attractive targets 
for spam and fraud, leading to a proliferation of sophisticated attacks. This 
trend is reflected in recent research, as papers 
have focused on identifying and classifying the various types of social media spam. 
Many of these studies employ techniques previously used to combat conventional 
email and web spam. SNSs also provide opportunities to take advantage of user 
reputation and other social graph-dependent features to improve classification. 
Nevertheless, most research has been carried out on publicly-available data 
from SNSs, making it unfeasible up until now to measure the effect of private user 
data on algorithms for detecting site misuse.

@@

Gao et al. \cite{gao} look at Facebook wall posts, analyzing temporal properties, 
URL characteristics, post ratios and other features of malicious accounts. They 
also pinpoint various spam ``campaigns" based on products advertised in a given 
time frame. They note that spam on Facebook often exhibits burstiness and is mainly 
sent from compromised accounts. Benevenuto et al. \cite{benevenuto} identify 
social attributes of spam and ham on video SNSs (in this case, YouTube), including video 
view counts, comment counts and user public profile attributes. They then use a 
support vector machine (SVM) for classification, yielding 96\% accuracy in detecting 
advertisers (``promoters"), but only accurately identifying 57\% of examples of more general spam.
